Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Additional table diagnostic

xtabs(~stats_class+math_science_research, data=ans.model)
# only one kid is doing research without a stats class
# recode to sum of them
ans.model$statsP <- with(ans.model, stats_class + math_science_research)

>>>>

xtabs(~stem+calc_1, data=ans.model)
# stem major is more associated with performance on lineups than calc 1...

xtabs(~stats_class+math_science_research, data=ans.model)
# only one kid is doing research without a stats class

# recode to sum of them
ans.model$statsP <- with(ans.model, stats_class + math_science_research)
